---
title: "R Bootcamp: Course 4"
author: "Elizabeth Chan"
date: "Sunday, May 9, 2021"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Text Formatting

I am writing a paragraph using plain text. The R Markdown makes use of YAML. I am using the following syntax to *italicise*, **bold**, superscript^2^, [hyperlink to my Github](https://github.com/echan1912) and write inline equations using Latex such as $y = m\mu + \sigma$.


* Here is an unordered list
* Name
     + Mamoru
     + Miyano

1. Here is an ordered list
2. Miyano's albums by release order
     + Break
     + Wonder
    
I use double tab indents for the sub-items.

## Tables

I manually enter a table like this

**Table 1:** Mean and Median for Speed and Distance

Variable|Mean |Median 
--------|-----|------ 
Speed   |15.40|15.0 
Distance|42.98|36.0

```{r}
library(knitr)
knitr::kable(anscombe, caption = "Anscombe's Quartet Data")
```

### Chunks
```{r}
summary(cars)
```

```{r, echo=FALSE}
plot(cars)
```

``I am going to report my R code inline by bracketing my work in two single quotes. For example, the mean speed was 15.4, *SD* = 5.29 with a sample size *n* = 50. ``

